---
title: "Why R is Magic Survey Report"
output: 
    html_document:
        css: style-report.css
        toc: true
        toc_depth: 2
        toc_float: true
        df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      include = TRUE,
                      warning = FALSE,
                      message = FALSE)
```

```{r}
# Load packages

library(tidyverse)
library(googlesheets4)
library(janitor)
library(lubridate)
library(tigris)
library(hrbrthemes)
library(tidygeocoder)
library(leaflet)
library(scales)

options(gargle_oauth_email = "david@rfortherestofus.com")
```

```{r include = FALSE}
# Set plotting default theme

theme_set(theme_ipsum(base_family = "Inter",
                      axis_title_family = "Inter",
                      grid_col = "transparent"))
```




```{r}
# Import our data
survey_responses_today <- read_sheet("https://docs.google.com/spreadsheets/d/1TcMCV2BuiBI_svmpFIAk0LTqBXNbXsrxZakYG8dG9dY/edit#gid=1229185329", 
                                     sheet = "Responses") %>% 
  # Make the variable names easy to work with
  clean_names() %>% 
  # Convert the timestamp into a date
  mutate(timestamp = as.Date(timestamp)) %>% 
  # Filter to only keep responses from today
  filter(timestamp == as_date(now()))

```

# About our Respondents

```{r}
number_of_responses <- nrow(survey_responses_today)

today_month <- month(now(),
                     label = TRUE,
                     abbr = FALSE) %>% 
  as.character()

today_day <- day(now()) %>% 
  as.character()

today_year <- year(now()) %>% 
  as.character()

today_pretty <- str_glue("{today_month} {today_day}, {today_year}")
```

We did a survey on `r today_pretty`. We received responses from `r number_of_responses` people. 



## Education

The education levels of respondents are below.

```{r fig.height=4}
survey_responses_today %>% 
  count(what_is_the_highest_level_of_education_you_have_completed) %>% 
  mutate(what_is_the_highest_level_of_education_you_have_completed = factor(what_is_the_highest_level_of_education_you_have_completed, levels = c("High school", "Associate's degree", "Bachelor's degree", "Master's degree", "Doctoral degree", "Other"))) %>% 
  mutate(what_is_the_highest_level_of_education_you_have_completed = fct_rev(what_is_the_highest_level_of_education_you_have_completed)) %>% 
  drop_na(what_is_the_highest_level_of_education_you_have_completed) %>% 
  ggplot(aes(what_is_the_highest_level_of_education_you_have_completed, n)) +
  geom_col(fill = "#6CABDD") +
  geom_text(aes(label = n),
            hjust = 2,
            color = "white") +
  coord_flip() +
  labs(title = "Education Levels of Respondents",
       x = NULL,
       y = NULL) +
  scale_y_continuous(breaks = pretty_breaks()) +
  theme(legend.position = "none", 
        axis.text.x = element_blank())
```


## Locations

Respondents listed the location of their primary residence. The map below shows their locations. 

```{r fig.height=6}
respondent_locations <- survey_responses_today %>% 
  drop_na(what_city_do_you_live_in) %>% 
  geocode(city = what_city_do_you_live_in,
          state = what_state_do_you_live_in,
          country = what_country_do_you_live_in,
          method = "osm") %>% 
  mutate(popup_text = str_glue("{what_city_do_you_live_in}, {what_state_do_you_live_in} {what_country_do_you_live_in}"))

leaflet(respondent_locations) %>% 
  addProviderTiles(providers$CartoDB.Positron) %>% 
  addCircleMarkers(~long, ~lat,
                   color = "#FF7400",
                   stroke = FALSE, 
                   fillOpacity = 0.7,
                   popup = ~popup_text,
                   clusterOptions = markerClusterOptions(showCoverageOnHover = FALSE))

```



# Familiarity with R

```{r}
mean_familiarity <- survey_responses_today %>% 
  summarize(mean_familiarity = mean(how_familiar_are_you_with_r, na.rm = TRUE)) %>% 
  mutate(mean_familiarity = round_half_up(mean_familiarity, 1)) %>% 
  pull(mean_familiarity)
```

On a 5-point scale, respondents listed their level of familiarity with R as `r number(mean_familiarity, .1)`. The figure below shows familiarity broken down by education level.

```{r fig.height = 4}
survey_responses_today %>% 
  drop_na(what_is_the_highest_level_of_education_you_have_completed) %>% 
  group_by(what_is_the_highest_level_of_education_you_have_completed) %>% 
  summarize(mean_familiarity = mean(how_familiar_are_you_with_r, na.rm = TRUE)) %>% 
  mutate(mean_familiarity = round_half_up(mean_familiarity, 1)) %>% 
  mutate(what_is_the_highest_level_of_education_you_have_completed = fct_relevel(what_is_the_highest_level_of_education_you_have_completed, levels = c("Bachelor's degree", "Master's degree", "Doctoral degree", "Other"))) %>% 
  mutate(what_is_the_highest_level_of_education_you_have_completed = fct_rev(what_is_the_highest_level_of_education_you_have_completed)) %>% 
  ggplot(aes(what_is_the_highest_level_of_education_you_have_completed, mean_familiarity)) +
  geom_col(fill = "#6CABDD") +
  geom_text(aes(label = number(mean_familiarity, .1)),
            hjust = 1.5,
            color = "white") +
  coord_flip() +
  scale_y_continuous(limits = c(0, 5),
                     breaks = seq(0, 5, by = 1)) +
  labs(title = "Familiarity with R\nby Education Level",
       x = NULL,
       y = NULL)  +
  theme(legend.position = "none", 
        axis.text.x = element_blank())
```



# Interest in Learning R

```{r}
mean_interest <- survey_responses_today %>% 
  summarize(mean_interest = mean(how_interested_are_you_in_learning_r, na.rm = TRUE)) %>% 
  mutate(mean_interest = round_half_up(mean_interest, 1)) %>% 
  pull(mean_interest)
```

On a 5-point scale, respondents listed their level of interest in learning R as `r number(mean_interest, .1)`.

```{r fig.height = 4}
survey_responses_today %>% 
  group_by(what_is_the_highest_level_of_education_you_have_completed) %>% 
  summarize(mean_interest = mean(how_interested_are_you_in_learning_r, na.rm = TRUE)) %>% 
  ungroup() %>% 
  mutate(mean_interest = round_half_up(mean_interest, 1)) %>% 
  mutate(what_is_the_highest_level_of_education_you_have_completed = factor(what_is_the_highest_level_of_education_you_have_completed,  levels = c("High school", "Associate's degree", "Bachelor's degree", "Master's degree", "Doctoral degree", "Other"))) %>% 
  drop_na(what_is_the_highest_level_of_education_you_have_completed) %>% 
 ggplot(aes(what_is_the_highest_level_of_education_you_have_completed, mean_interest)) +
  geom_col(fill = "#6CABDD") +
  geom_text(aes(label = number(mean_familiarity, .1)),
            hjust = 1.5,
            color = "white") +
  coord_flip() +
  scale_y_continuous(limits = c(0, 5),
                     breaks = seq(0, 5, by = 1)) +
  labs(title = "Interest in Learning R\nby Education Level",
       x = NULL,
       y = NULL)  +
  theme(legend.position = "none", 
        axis.text.x = element_blank())
```


